Comparing human and model-based forecasts of COVID-19 in Germany and Poland

### 2021-10-15 manuscript/manuscript.Rmd
update author list
remove old author statement

---
title: "Comparing human and model-based forecasts of COVID-19 in Germany and Poland"
output: 
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
    keep_tex:  true
bibliography:
  - references.bib
  - GermanPolishpaper.bib
---

*Anonymous Alpaca and many friends*

>>>>

---
title: "Comparing human and model-based forecasts of COVID-19 in Germany and Poland"
output: 
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
    keep_tex:  true
    toc: false
bibliography:
  - references.bib
  - GermanPolishpaper.bib
---

Target journal: eLife

*Nikos I. Bosse, Sam Abbott, Johannes Bracher, Habakuk Hain, Billy Quilty, CMMID Working Group, Edwin van Leeuwen, Anne Cori, Sebastian Funk*
